### 2020-12-20 paper/localpsf.tex
adding back algorithm for point selection

Ideally, sample points $x_i$ and $x_j$ should be far enough apart from each other that the supports of $\left\langle\mathcal{A}, \delta_{x_i}\right\rangle^*$ and $\left\langle\mathcal{A}, \delta_{x_j}\right\rangle^*$ do not overlap. Since it is too expensive compute the support of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ directly, we instead estimate that the support of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ is contained in the ellipsoid
\begin{equation*}
	E_x := \{x' \in \Omega: (x' - \mu(x))^T \Sigma(x)^{-1} (x' - \mu(x)) \le \tau^2\},
\end{equation*}
where $\tau$ is a small number of standard deviations; we use $\tau=3$. The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations of the mean for the Gaussian distribution that has the same mean and covariance as $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$. The fraction of the mass of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ residing outside of $E_x$ is less than $1/\tau^2$ by Chebyshev's inequality, though we find this bound is conservative and far less mass resides in this region in practice. 
%We call $E_x$ the \emph{unit ellipsoid} with mean $\mu(x)$ and covariance $\Sigma(x)/\tau^2$.

@@

%\begin{algorithm2e}
%	\SetAlgoNoLine
%	\SetKwInOut{Input}{Input}
%	\SetKwProg{Fn}{Function}{}{}
%
%	Start with a finite set of candidate points $P \subset \Omega_I$
%	
%	$S_b \gets \{\}$
%	
%	\While{$P$ is not empty}{
%		Pick a random point $p \in P$ and remove $p$ from $P$
%		
%		$p\text{\_is\_acceptable} \gets \text{True}$
%		
%		\For{$q \in S_b$}{
%			
%			\If{$E_p \cap E_q \neq \{\}$}{
%				
%				$p\text{\_is\_acceptable} \gets \text{False}$
%				
%				Terminate for loop
%			}
%		}
%	
%		\If{$p\text{\_is\_acceptable}$}{
%			
%			$S_b \gets S_b \cup \{p\}$
%			
%			$P \gets P \setminus \{q \in P : \mu(q) \in E_p\}$
%		}
%	}
%
%	\caption{Choosing one batch of sample points, $S_b$}
%	\label{alg:point_choice}
%\end{algorithm2e}

>>>>

Ideally, sample points $x_i$ and $x_j$ should be far enough apart from each other that the supports of $\left\langle\mathcal{A}, \delta_{x_i}\right\rangle^*$ and $\left\langle\mathcal{A}, \delta_{x_j}\right\rangle^*$ do not overlap. Since it is too expensive compute the support of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ directly, we instead estimate that the support of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ is contained in the ellipsoid
\begin{equation}
\label{eq:support_ellipsoid}
	E_x := \{x' \in \Omega: (x' - \mu(x))^T \Sigma(x)^{-1} (x' - \mu(x)) \le \tau^2\},
\end{equation}
where $\tau$ is a small number of standard deviations; we use $\tau=3$. The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations of the mean for the Gaussian distribution that has the same mean and covariance as $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$. The fraction of the mass of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ residing outside of $E_x$ is less than $1/\tau^2$ by Chebyshev's inequality, though we find this bound is conservative and far less mass resides in this region in practice. 
%We call $E_x$ the \emph{unit ellipsoid} with mean $\mu(x)$ and covariance $\Sigma(x)/\tau^2$.

@@

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwProg{Fn}{Function}{}{}

	Start with a finite set of candidate points $P \subset \Omega_I$

	Initialize new empty batch of sample points, $S_b$

	\While{$P$ is not empty}{
		Determine the point $p \in P$ that is farthest from all points in previous sample point batches

		Remove $p$ from $P$

		\If{$\text{point\_is\_acceptable}(p, S_b)$}{

			Add $p$ to $S_b$

			Remove all points $q$ with $\mu(q) \in E_p$ from $P$
		}
	}

    \SetKwFunction{FMain}{point\_is\_acceptable}
\SetKwProg{Fn}{Function}{:}{}
\Fn{\FMain{$p$, $S_b$}}{

	$p\text{\_is\_acceptable} \gets \text{True}$

	$E_p$ is the ellipsoid associated with $p$ (see \eqref{eq:support_ellipsoid})

	\For{$q \in S_b$}{

		$E_q$ is the ellipsoid associated with $q$

		\If{$E_p \cap E_q \neq \{\}$}{

			$p\text{\_is\_acceptable} \gets \text{False}$

			Terminate for loop
		}
	}
	\textbf{return} $p\text{\_is\_acceptable}$ 
}

	\caption{Choosing one batch of sample points, $S_b$}
	\label{alg:point_choice}
\end{algorithm2e}
